PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

html_notebook:
  theme: cerulean
toc: yes

params:
  glad.dem.raw: edgi.dem.raw

---

@@

# Specify cohort
```{r Specify cohort}
GLAD = TRUE
EDGI = FALSE
NBR = FALSE
RAMP = FALSE
```

@@

Select respiratory variables
```{r coping edgi respiratory cleaning}
if(EDGI == TRUE){
coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    respiratory.breath_diarrhoea_fatigue_fever,
    respiratory.worst_ill_feel,
    respiratory.persistent_cough,
    respiratory.skipping_meals_because_you_felt_unwell,
    respiratory.was_your_sense_of_smell_impaired,
    respiratory.was_your_sense_of_taste_impaired,
    respiratory.feeling_tiredfatigued,
    respiratory.throat_swab_coronavirus_nose,
    respiratory.throat_swab_test_nose,
    respiratory.coronavirus_antibody_test,
    respiratory.results_antibody_test
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

html_notebook:
  theme: cerulean
toc: yes
---

@@

# Specify cohort
```{r Specify cohort}
GLAD = FALSE
EDGI = TRUE
NBR = FALSE
RAMP = FALSE
```

@@

Select respiratory variables
```{r coping edgi respiratory cleaning}
if(EDGI == TRUE){
coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
    respiratory.worst_ill_feel,
    respiratory.persistent_cough,
    respiratory.skipping_meals_because_you_felt_unwell,
    respiratory.was_your_sense_of_smell_impaired,
    respiratory.was_your_sense_of_taste_impaired,
    respiratory.feeling_tiredfatigued,
    respiratory.throat_swab_coronavirus_nose,
    respiratory.throat_swab_test_nose,
    respiratory.coronavirus_antibody_test,
    respiratory.results_antibody_test
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
